%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    %---------------------------------------------------------
    \cventry
    {L3 Engineer} % Job title
    {Wizeline (Client: ClearBank)} % Organization
    {} % Location
    {September 2025 - Present} % Date(s)
    {
        \begin{cvitems}
            \item {Technical ownership of an Azure microservices domain with end-to-end responsibility: design, implementation, deployment, and operations (stability, evolution, and production support).}
            \item {Continuous .NET stack modernization (microservice migrations to modern .NET/.NET Core), applying compatibility, performance, quality, and observability standards for banking environments.}
            \item {Design and implementation of REST APIs and distributed components, including asynchronous integration with Azure Service Bus for decoupling, scalability, and resilience.}
            \item {Deployment and operation of services on AKS (Azure Kubernetes Service), actively contributing to progressive Kubernetes migration and standardizing releases with Helm.}
            \item {Cloud provisioning and governance through Infrastructure as Code (Terraform): resource, network, and security management with controlled, traceable changes aligned with strict approval processes.}
            \item {Continuous contribution to CI/CD with Azure DevOps: pipeline evolution, multi-environment deployments (test/pre-production/production), rollback strategies, and telemetry-based post-deploy verification.}
            \item {Daily operations and troubleshooting: analysis of traces, metrics, and dependencies with native Azure tooling (Application Insights, Azure Monitor, Log Analytics), incident diagnosis, and reliability optimization.}
            \item {On-call rotations: end-to-end incident handling (triage, identifier-based correlation, evidence/payload analysis in Storage/Blobs when needed) and closure with post-mortem/RCA and corrective/preventive actions.}
            \item {\textbf{Technologies}: C\#, .NET (Core/modern .NET), Azure (AKS, Service Bus, Storage/Blobs, Azure SQL), Terraform, Helm, Azure DevOps, Application Insights, Azure Monitor, Log Analytics.}
        \end{cvitems}
    }
    %---------------------------------------------------------
    %---------------------------------------------------------
    \cventry
    {Full Stack Developer} % Job title
    {Servantrip} % Organization
    {Avilés - Remote} % Location
    {July 2024 - August 2025} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Architecture and development of .NET 8 microservices for high-scale B2B applications (5M+ daily transactions).}
            \item {Design and implementation of event-driven architecture using Azure Service Bus and CQRS patterns.}
            \item {Leadership in critical external API integrations and distributed services orchestration.}
            \item {Implementation of CI/CD pipelines with Azure DevOps, including automated Docker container deployments.}
            \item {Performance optimization and scalability of microservices with distributed monitoring and health checks.}
            \item {Cloud infrastructure management in Azure (AKS, Container Instances, Application Insights).}
            \item {Key participation in distributed systems architecture decisions and DevOps standards compliance.}
            \item {Resolution of high-complexity problems in microservices and distributed systems environments.}
        \end{cvitems}
    }
    %---------------------------------------------------------
    \cventry
    {Full Stack Developer} % Job title
    {CyC} % Organization
    {Pamplona - Remote} % Location
    {November 2023 - July 2024} % Date(s)
    {
        \begin{cvitems}
            \item {Back-end development in C\# and SQL database management for the Navarra Health System.}
            \item {Collaborative work in state structures and coordination with multidisciplinary teams.}
            \item {Quality assurance through comprehensive integration testing.}
        \end{cvitems}
    }
    %---------------------------------------------------------
    \cventry
    {Full Stack Developer} % Job title
    {Clarcat} % Organization
    {Gijón} % Location
    {June 2022 - October 2023} % Date(s)
    {
        \begin{cvitems}
            \item {Architecture and comprehensive implementation of cloud-native digital platform in .NET for digital transformation of metallurgical industrial parks.}
            \item {Design and implementation of complete CI/CD pipelines with Azure DevOps, including automated deployment and testing.}
            \item {Development of microservices architecture with Docker containers and orchestration in Azure Container Instances.}
            \item {Implementation of Infrastructure as Code (IaC) with Terraform for cloud resource management.}
            \item {Management of scalable full-stack solutions with monitoring and observability in Azure.}
            \item {Interdepartmental coordination and technical leadership in DevOps methodologies and continuous integration culture.}
        \end{cvitems}
    }
 %---------------------------------------------------------
    \cventry
    {Full Stack Developer} % Job title
    {Bar Playa de Porcía} % Organization
    {El Franco, Asturias, Spain} % Location
    {April 2022 - Present} % Date(s)
    {
        \begin{cvitems}
            \item {Website development with WordPress, reaching approximately 5,000 monthly visits after SEO and web analytics improvements.}
            \item {Implementation of advanced analytics solutions using Google Analytics and Power BI for sales forecasting and capacity control.}
            \item {Mobile performance and web accessibility optimization.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Data Engineer, Power BI} % Job title
{Babel} % Organization
{Aviles, Asturias, Spain} % Location
{December 2021 - January 2022} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Use of Power BI for report generation.}
        \item  {Integration with Azure cloud}
        \item {Data processing, both online and locally}
        \item {Use of PowerQuery for data processing}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Junior C++ Programmer} % Job title
{SOGETI, working for HP} % Organization
{Langreo, Asturias, Spain} % Location
{February 2021 - December 2021} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance and creation of functionalities in MV (mid volume, i.e., industrial) printers.
                    Both solid support and textile.}
        \item {Use of C++ for software development.}
        \item {Creation and use of static and dynamic libraries.}
        \item {Use of TCL and state machines.}
        \item {Use of Subversion for work development.}
        \item {Pair programming in large teams around the world.}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Administrator (company internship)} % Job title
{ASAC} % Organization
{Asturias, Spain} % Location
{February. 2021 - March 2021} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Company internship at a Tier 3 Datacenter. Working with specific server hardware.}
        \item {Documentation of procedures and interaction with clients.}
    \end{cvitems}
}



%---------------------------------------------------------
\cventry
{IT Services Collaboration Intern} % Job title
{University of Oviedo} % Organization
{Oviedo, Asturias} % Location
{September 2019 - July 2021} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance of the university's local systems.}
        \item {Cloning, installation, and hardware updates for university equipment.}
    \end{cvitems}
}

%---------------------------------------------------------

\end{cventries}
