%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    
    %---------------------------------------------------------
\cventry
{Full Stack developer} % Job title
{Clarcat} % Organization
{Gijón} % Location
{June 2022 - Present} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {.Net project for a major multinational company.}
        \item {Fully integrated in Azure DevOps}
        \item {Management of UI, Back-end, and Database}
        \item {Use of agile methodologies}
        \item {Great teamwork and collaboration with other departments}
    \end{cvitems}
}
 %---------------------------------------------------------
\cventry
{Full Stack developer} % Job title
{bar Playa de Porcía} % Organization
{El Franco, Asturias, Spain} % Location
{April 2022 - Present} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creation of the bar website using Wordpress}
        \item  {Integration with Google Analytics}
        \item {Data processing for sales and capacity prediction}
        \item {SEO positioning}
        \item {Mobile accessibility requirements}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Data Engineer, Power BI} % Job title
{Babel} % Organization
{Aviles, Asturias, Spain} % Location
{December 2021 - January 2022} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Use of Power BI for report generation.}
        \item  {Integration with Azure cloud}
        \item {Data processing, both online and locally}
        \item {Use of PowerQuery for data processing}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Junior C++ Programmer} % Job title
{SOGETI, working for HP} % Organization
{Langreo, Asturias, Spain} % Location
{February 2021 - December 2021} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance and creation of functionalities in MV (mid volume, i.e., industrial) printers.
                    Both solid support and textile.}
        \item {Use of C++ for software development.}
        \item {Creation and use of static and dynamic libraries.}
        \item {Use of TCL and state machines.}
        \item {Use of Subversion for work development.}
        \item {Pair programming in large teams around the world.}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Administrator (company internship)} % Job title
{ASAC} % Organization
{Asturias, Spain} % Location
{February. 2021 - March 2021} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Company internship at a Tier 3 Datacenter. Working with specific server hardware.}
        \item {Documentation of procedures and interaction with clients.}
    \end{cvitems}
}



%---------------------------------------------------------
\cventry
{IT Services Collaboration Intern} % Job title
{University of Oviedo} % Organization
{Oviedo, Asturias} % Location
{September 2019 - July 2021} % Date(s)
{
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance of the university's local systems.}
        \item {Cloning, installation, and hardware updates for university equipment.}
    \end{cvitems}
}

%---------------------------------------------------------

\end{cventries}
