%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Simple Cover Letter Template

\documentclass[11pt, a4paper]{article}

% Basic packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{fancyhdr}

% Page layout
\geometry{left=1.4cm, top=1.4cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Colors
\definecolor{awesome-red}{HTML}{DC3522}
\colorlet{awesome}{awesome-red}

% Font configuration - Using standard fonts to avoid issues
\setmainfont{TeX Gyre Termes}
\setsansfont{TeX Gyre Heros}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize Alejandro Iglesias Calvo --- Cover Letter}

% Section formatting
\newenvironment{cvletter}{\begin{flushleft}}{\end{flushleft}}
\newcommand{\lettersection}[1]{%
  \vspace{8pt}%
  \color{awesome}\large\bfseries #1%
  \color{black}\\[1pt]\hrule\vspace{4pt}%
}

% Begin document
\begin{document}

% Header with personal information
\begin{minipage}[t]{1.0\textwidth}
  \begin{center}
    {\LARGE\bfseries Alejandro Iglesias Calvo}\\[5pt]
    {\large\textcolor{awesome}{Full Stack Developer}}\\[5pt]
    {\small Calle fraternidad, Oviedo, Asturias, España}
    \vspace{10pt}
    
    \begin{tabular}{@{}ll@{}}
      Phone: & +34 717 719 965 \\
      Email: & \href{mailto:alejandroiglesiascalvo@hotmail.com}{alejandroiglesiascalvo@hotmail.com} \\
      GitHub: & \href{https://github.com/AlejandroIglesiasCalvo}{AlejandroIglesiasCalvo} \\
      LinkedIn: & \href{https://linkedin.com/in/alejandro-iglesias-calvo}{alejandro-iglesias-calvo}
    \end{tabular}
  \end{center}
\end{minipage}

\vspace{20pt}

% Recipient information
Company Recruitment Team

\vspace{10pt}

% Date
\today

\vspace{20pt}

% Letter opening
Dear reader of this presentation,

\vspace{10pt}

% Letter content
\begin{cvletter}
  \lettersection{About Me}
  I am insightful, tenacious and curious. I am always interested in learning, and improving. I like to understand, and make sense of things. The more I understand something, the easier it is for me to learn new things.

  \lettersection{Why 5CA?}
  I consider that this is a good opportunity to work, due to the wide range of projects that your company has, and its size. I would like to enter a new project, grow within the company, and be useful.

  \lettersection{Why Me?}
  I am looking for a good remote job, where I can give my best, and build a good future for myself.
\end{cvletter}

% Letter closing
\vspace{10pt}
Sincerely,

\vspace{20pt}

Alejandro Iglesias Calvo

\vspace{10pt}

\small Attached: Curriculum Vitae

\end{document}
